### 2015-01-27 paper.tex
add ref to kimmo

>>>>

This set would be disambiguated by a syntactic constraint that would
select subject if followed by a finite verb form.

\cite{koskenniemi92} include also clause boundaries (TODO read about
it), such as marking coordinated or subordinated clauses, or showing
beginning and end of an embedded clause.
%; so the parse would be complete if \emph{the} and \emph{bear} would belong to

(c/p from koskenniemi paper)
``Rules in the CG formalism are typically dedicated
for one of the above tasks, and they are
executed as successive groups.
In finite-state syntax, rules are logically unordered.''
